---
title: "Sim Project"
author: "Frank D'Ambrosio"
date: "11/04/2021"
output: html_document
---

package
```{r}
library(itertools)
library(tidyverse)
library(ggplot2)
library(plyr)
```

sd.game returns players and drinks  
sd.game2 returns the dealer at the end of the game  
sd.game3 returns list of drinks for each player at the end of the game  
last chunk plots players and drinks, prints out probability of ending as dealer  
and calculates each players bac  



create a deck
```{r}

deck <- c(rep(c("2", "3", "4", "5", "6", "7", "8", "9", "10", "J", "Q", "K", "A"),4))
full.deck <- deck #
#sample(deck)

```

players
```{r}
n <- 6
# for (i in 1:n) {
#   cat("Player",i, " " )
#   
# }

#n <- 6
players <- vector()

for (i in 1:n) {
  players[i] <- i
  # cat("Player",i, " " )
}
players

#drink tally

drinks <- vector()
for (i in 1:n) {
  drinks[i] <- 0
  
}

drinks

# drinks[active.player] <- 1
# drinks
totals <- cbind(players,drinks)
totals

```

pick a dealer
```{r}
dealer <- sample(players,1)
dealer

```

starting player/active player
```{r}
active.player <- players[dealer+1]

if(active.player > n){
  active.player <- 1
}

```


move dealer to next person
```{r}
wrong <- 3
dealer
if (wrong == 3) {
  if (dealer == players[n]) {
    dealer <- players[1]
    
  }
  else{
    dealer <- players[dealer+1]
    
  }
  wrong <- 0
}
```


active player cant = dealer
```{r}

if(dealer == active.player){
  active.player <- active.player[active.player + 1]
}


```



turns
```{r}


wrong <- 0

turn <- function() {

  shuffled.deck <- sample(deck)
  card <- shuffled.deck[1]
  guess <- sample(shuffled.deck, 1)
  if (guess == card) {
    wrong <- 0
    shuffled.deck <- shuffled.deck[-1]
    drinks[dealer] <- 1 + drinks[dealer]
  }
  else{ #(guess != card){
    remaining <- subset(shuffled.deck, shuffled.deck != guess)
    guess2 <- sample(remaining , 1)
    
    
    if (guess2 == card) {
      wrong <- 0
      shuffled.deck <- shuffled.deck[-1]
      drinks[dealer] <- 1 + drinks[dealer]
    }
    else{#if(guess2 != card){
      
      wrong <- wrong + 1
      shuffled.deck <- shuffled.deck[-1]
      drinks[active.player] <- drinks[active.player] + 1
    }
 return(totals) }
  
}
turn()



```


game
```{r}
shuffled.deck <- 0
totals <- 0
guess <- 0
guess2 <- 0
deck <- 0
drinks <- 0
wrong <- 0




game <- function(n) {
  #set up the game
    deck <-
    c(rep(
      c("2", "3", "4", "5", "6", "7", "8", "9", "10", "J", "Q", "K", "A"),
      4
    ))
  
  shuffled.deck <- sample(deck)
  
  players <- vector()
  
  for (i in 1:n) {
    players[i] <- i
  }
  
  drinks <- vector()
  for (i in 1:n) {
    drinks[i] <- 0
    
  }
  
  totals <- cbind(players, drinks)
  
  dealer <- sample(players, 1)
  
  rp <- setdiff(players, dealer)
  
  active.player <- sample(rp,1)

  
  wrong <- 0
  
  n.cards <- 52
  
  while (n.cards >2) {
    ##turn starts here
    card <- shuffled.deck[1]
    guess <- sample(shuffled.deck, 1)
    
    if (guess == card) {
      wrong <- 0
      shuffled.deck <- shuffled.deck[-1]
      drinks[dealer] <- 1 + drinks[dealer]
    }
    else{
      # if (guess != card) {
      remaining <- subset(shuffled.deck, shuffled.deck != guess)
      guess2 <- sample(remaining , 1)
      
      if (guess2 == card) {
        wrong <- 0
        shuffled.deck <- shuffled.deck[-1]
        drinks[dealer] <- 1 + drinks[dealer]
      }
      else{
        #if(guess2 != card){
        
        wrong <- wrong + 1
        shuffled.deck <- shuffled.deck[-1]
        drinks[active.player] <- 1 + drinks[active.player] 
      }
    }
    #1 turn
    
    
    n.cards <- n.cards - 1
    
    active.player <- active.player[+1]
    
    if(active.player > n){
      active.player <- players[1]
    }
    
    #dealer management
    if (wrong == 3) {
      if (dealer == n) {
        dealer <- 1
        
      }
      else{
        dealer <- players[dealer] + 1
        
      }
      wrong <- 0
    }
    #go to next active player
    
    if(dealer == active.player){
      active.player <- active.player + 1
    }
    
    if(active.player > n){
      active.player <- 1
    }

      
      
      #active player and dealer cant be the same
  }
  if(n.cards == 2){
    drinks[dealer] <- 2 + drinks[dealer]
  }
  drinks <- drinks + 13 #everytime the 4th card appears everyone drink so we are gonna add 13 to all drink totals
    
    
 totals <- cbind(players, drinks)
 totals.df <- as.data.frame(cbind(players,drinks))
  return(totals.df)
  }
 
  


game(8)

```

replicate and look at distribution
```{r}
g <- replicate(10, game(8))

#g
```

plot this
```{r}
n_sim <- 10000
n_play <- 8
g_list <- list()
for(i in 1:n_sim) {
  g_list[[i]] <- data.frame(game(n_play))
  g_list[[i]]$sim_num <- i 
}

g_df <- do.call(rbind, g_list)


ggplot(data = g_df, aes(drinks)) +
  geom_histogram( bins=50) +
  facet_wrap(~ players)

ggplot(data = g_df, aes(players, drinks, group = players)) +
  geom_boxplot()

```


lets see what happens when we designate a starting dealer
```{r}

shuffled.deck <- 0
totals <- 0
guess <- 0
guess2 <- 0
deck <- 0
drinks <- 0
wrong <- 0




sd.game <- function(n,sd) {
  #set up the game
  if(sd<1 | sd>n){
    return("Invalid Starting Dealer")
  }
    deck <-
    c(rep(
      c("2", "3", "4", "5", "6", "7", "8", "9", "10", "J", "Q", "K", "A"),
      4
    ))
  
  shuffled.deck <- sample(deck)
  
  players <- vector()
  
  for (i in 1:n) {
    players[i] <- i
  }
  
  drinks <- vector()
  for (i in 1:n) {
    drinks[i] <- 0
    
  }
  
  totals <- cbind(players, drinks)
  
  dealer <- sd
  
  rp <- setdiff(players, dealer)
  
  active.player <- sample(rp,1)

  
  wrong <- 0
  
  n.cards <- 52
  
  while (n.cards >2) {
    ##turn starts here
    card <- shuffled.deck[1]
    guess <- sample(shuffled.deck, 1)
    
    if (guess == card) {
      wrong <- 0
      shuffled.deck <- shuffled.deck[-1]
      drinks[dealer] <- 1 + drinks[dealer]
    }
    else{
      # if (guess != card) {
      remaining <- subset(shuffled.deck, shuffled.deck != guess)
      guess2 <- sample(remaining , 1)
      
      if (guess2 == card) {
        wrong <- 0
        shuffled.deck <- shuffled.deck[-1]
        drinks[dealer] <- 1 + drinks[dealer]
      }
      else{
        #if(guess2 != card){
        
        wrong <- wrong + 1
        shuffled.deck <- shuffled.deck[-1]
        drinks[active.player] <- 1 + drinks[active.player] 
      }
    }
    #1 turn
    
    
    n.cards <- n.cards - 1
    
    active.player <- active.player[+1]
    
    if(active.player > n){
      active.player <- players[1]
    }
    
    #dealer management
    if (wrong == 3) {
      if (dealer == n) {
        dealer <- 1
        
      }
      else{
        dealer <- players[dealer] + 1
        
      }
      wrong <- 0
    }
    #go to next active player
    
    if(dealer == active.player){
      active.player <- active.player + 1
    }
    
    if(active.player > n){
      active.player <- 1
    }

      
      
      #active player and dealer cant be the same
  }
  if(n.cards == 2){
    drinks[dealer] <- 2 + drinks[dealer]
  }
    drinks <- drinks + 13
    #ends here
 totals <- cbind(players, drinks, dealer)
 totals.df <- as.data.frame(cbind(players,drinks))
  return(totals)
  }
 
sd.game(7,5)

```

lets plot this now
```{r}
n_sim <- 10000
n_play <- 7
g_list <- list()
for(i in 1:n_sim) {
  g_list[[i]] <- data.frame(sd.game(n_play,5))
  g_list[[i]]$sim_num <- i 
}

g_df <- do.call(rbind, g_list)


ggplot(data = g_df, aes(drinks)) +
  geom_histogram( bins=50) +
  facet_wrap(~ players)

ggplot(data = g_df, aes(players, drinks, group = players)) +
  geom_boxplot()

ggplot(data = g_df, aes(dealer)) +
  geom_histogram( bins=30) +
  facet_wrap(~ players)


```
probability of being dealer at end of game
```{r}
#sd.game2 is for returning the dealer at the end of the game
sd.game2 <- function(n,sd) {
  #set up the game
  if(sd<1 | sd>n){
    return("Invalid Starting Dealer")
  }
    deck <-
    c(rep(
      c("2", "3", "4", "5", "6", "7", "8", "9", "10", "J", "Q", "K", "A"),
      4
    ))
  
  shuffled.deck <- sample(deck)
  
  players <- vector()
  
  for (i in 1:n) {
    players[i] <- i
  }
  
  drinks <- vector()
  for (i in 1:n) {
    drinks[i] <- 0
    
  }
  
  totals <- cbind(players, drinks)
  
  dealer <- sd
  
  rp <- setdiff(players, dealer)
  
  active.player <- sample(rp,1)

  
  wrong <- 0
  
  n.cards <- 52
  
  while (n.cards >2) {
    ##turn starts here
    card <- shuffled.deck[1]
    guess <- sample(shuffled.deck, 1)
    
    if (guess == card) {
      wrong <- 0
      shuffled.deck <- shuffled.deck[-1]
      drinks[dealer] <- 1 + drinks[dealer]
    }
    else{
      # if (guess != card) {
      remaining <- subset(shuffled.deck, shuffled.deck != guess)
      guess2 <- sample(remaining , 1)
      
      if (guess2 == card) {
        wrong <- 0
        shuffled.deck <- shuffled.deck[-1]
        drinks[dealer] <- 1 + drinks[dealer]
      }
      else{
        #if(guess2 != card){
        
        wrong <- wrong + 1
        shuffled.deck <- shuffled.deck[-1]
        drinks[active.player] <- 1 + drinks[active.player] 
      }
    }
    #1 turn
    
    
    n.cards <- n.cards - 1
    
    active.player <- active.player[+1]
    
    if(active.player > n){
      active.player <- players[1]
    }
    
    #dealer management
    if (wrong == 3) {
      if (dealer == n) {
        dealer <- 1
        
      }
      else{
        dealer <- players[dealer] + 1
        
      }
      wrong <- 0
    }
    #go to next active player
    
    if(dealer == active.player){
      active.player <- active.player + 1
    }
    
    if(active.player > n){
      active.player <- 1
    }

      
      
      #active player and dealer cant be the same
  }
  if(n.cards == 2){
    drinks[dealer] <- 2 + drinks[dealer]
  }
    drinks <- drinks + 13
    #ends here
 totals <- cbind(players, drinks, dealer)
 totals.df <- as.data.frame(cbind(players,drinks))
  return(dealer)
}

prop.table(table(replicate(10000, sd.game2(7,5))))


```




pounds to kg
```{r}

pounds.to.g <- function(lbs){
  g <- lbs*454
  return(g)
}

pounds.to.g(150)


```

average grams per drink
```{r}
alc <- function(drinks){
  alc.amnt <- drinks*1.4 #this is total alcohol in grams assuming 14 per full drink(ie 1 whole beer) and 1 full drink takes 10 drinks to finish. I did this with a drink taking 8 drinks to finish and the bac levels were a little higher than id expect but this game CAN do that to you
  return(alc.amnt)
  
}

alc(15)

#https://www.wikihow.com/Calculate-Blood-Alcohol-Content-(Widmark-Formula)

```

bmi calc
```{r}

#for now lets average male and female constant for this calculation
constant <- (.55+.68)/2
constant

#
bac.formula <- function(alc.amnt, g){
  bac <- (alc.amnt/(g*constant))*100
  return(bac)
}

bac.formula(26.25, 68100)

```

bac.comb
```{r}
bac.comb <- function(drinks,lbs,s){
  if(s == 1){
    constant <- .68 #constant for males
  }
  else if(s == 2){
    constant <- .55 #constant for females
  }else{
    return("invalid input for s") #i dont have any data for other genders' constant for bac calculation
  }
  
  bac <- (alc(drinks)/(pounds.to.g(lbs)*constant) ) *100
  
  return(bac)
  
}

bac.comb(22,150,1)
```

```{r}

#sd.game3 is to return total drinks
sd.game3 <- function(n,sd) {
  #set up the game
  if(sd<1 | sd>n){
    return("Invalid Starting Dealer")
  }
    deck <-
    c(rep(
      c("2", "3", "4", "5", "6", "7", "8", "9", "10", "J", "Q", "K", "A"),
      4
    ))
  
  shuffled.deck <- sample(deck)
  
  players <- vector()
  
  for (i in 1:n) {
    players[i] <- i
  }
  
  drinks <- vector()
  for (i in 1:n) {
    drinks[i] <- 0
    
  }
  
  totals <- cbind(players, drinks)
  
  dealer <- sd
  
  rp <- setdiff(players, dealer)
  
  active.player <- sample(rp,1)

  
  wrong <- 0
  
  n.cards <- 52
  
  while (n.cards >2) {
    ##turn starts here
    card <- shuffled.deck[1]
    guess <- sample(shuffled.deck, 1)
    
    if (guess == card) {
      wrong <- 0
      shuffled.deck <- shuffled.deck[-1]
      drinks[dealer] <- 1 + drinks[dealer]
    }
    else{
      # if (guess != card) {
      remaining <- subset(shuffled.deck, shuffled.deck != guess)
      guess2 <- sample(remaining , 1)
      
      if (guess2 == card) {
        wrong <- 0
        shuffled.deck <- shuffled.deck[-1]
        drinks[dealer] <- 1 + drinks[dealer]
      }
      else{
        #if(guess2 != card){
        
        wrong <- wrong + 1
        shuffled.deck <- shuffled.deck[-1]
        drinks[active.player] <- 1 + drinks[active.player] 
      }
    }
    #1 turn
    
    
    n.cards <- n.cards - 1
    
    active.player <- active.player[+1]
    
    if(active.player > n){
      active.player <- players[1]
    }
    
    #dealer management
    if (wrong == 3) {
      if (dealer == n) {
        dealer <- 1
        
      }
      else{
        dealer <- players[dealer] + 1
        
      }
      wrong <- 0
    }
    #go to next active player
    
    if(dealer == active.player){
      active.player <- active.player + 1
    }
    
    if(active.player > n){
      active.player <- 1
    }

      
      
      #active player and dealer cant be the same
  }
  if(n.cards == 2){
    drinks[dealer] <- 2 + drinks[dealer]
  }
    drinks <- drinks + 13
    #ends here
 totals <- cbind(players, drinks, dealer)
 totals.df <- as.data.frame(cbind(players,drinks))
  return(drinks)
  }


n <- 7
weight.list <- c(105,111,128,155,168,185,215) #random list of weights lbs

s.list <- c(2,2,2,2,1,1,1) #random list of sex of players
# weight.list
# s.list
drink_list <- c(34,19,16,16,16,22,20)


bac.list <- list()

for(i in 1:n){
  bac.list[i] <- 0
  bac.list[i] <- bac.comb(sd.game3(7,5)[i], weight.list[i], s.list[i])
}

#drink_list[[i]] <- data.frame(sd.game(n_play,5))
cbind(bac.list)
#sd.game(7,5)




bac.list.avg <- list()
for(i in 1:n){
  bac.list.avg[i] <- 0
  bac.list.avg[i] <- bac.comb(mean(replicate(1000,sd.game3(7,5))[i]),weight.list[i], s.list[i])
}
cbind(bac.list.avg)
```

```{r}

weight.list <- c(105,111,128,155,168,185,215) #random list of weights lbs

s.list <- c(2,2,2,2,1,1,1) #random list of sex of players

#can change values of the above 2 lists for the function below





bac.results <- function(n, sd) {
  weight.list <- floor(runif(n, 105, 225))#this is for randomization but can be specified
  s.list <- sample(1:2, n , replace = T)#this is for randomization but can be specified
  
  bac.list <- list()
  
  for (i in 1:n) {
    bac.list[i] <- 0
    bac.list[i] <-
      bac.comb(sd.game3(7, 5)[i], weight.list[i], s.list[i])
  }
  bac.list.avg <- list()
  for (i in 1:n) {
    bac.list.avg[i] <- 0
    bac.list.avg[i] <-
      bac.comb(mean(replicate(1000, sd.game3(n, sd))[i]), weight.list[i], s.list[i])
  }
  return(cbind(cbind(bac.list), cbind(bac.list.avg), s.list, weight.list))
}

bac.results(7,5)
```


```{r}
set.seed(8675309)

###GG plots
n_sim <- 10000
n <- 7
g_list <- list()
for(i in 1:n_sim) {
  g_list[[i]] <- data.frame(sd.game(n,5))
  g_list[[i]]$sim_num <- i 
}

g_df <- do.call(rbind, g_list)


ggplot(data = g_df, aes(drinks)) +
  geom_histogram( bins=50) +
  facet_wrap(~ players)

ggplot(data = g_df, aes(players, drinks, group = players)) +
  geom_boxplot()

ggplot(data = g_df, aes(dealer)) +
  geom_histogram( bins=30) +
  facet_wrap(~ players)
###



###probability of being dealer at end of game
cat("Probability of being dealer at the end of the game",rbind(1:n,prop.table(table(replicate(10000, sd.game2(7,5))))), sep = "
")

###bac results at end of game
bac.results(7,5)
```












